\documentclass{article}
\usepackage{metric-min}
%\usepackage{showkeys}
\hypersetup{pdftitle={Correction to: Metric minimizing surfaces},
pdfauthor={Anton Petrunin}}

\begin{document}

\title{Correction to: Metric minimizing surfaces}
\author{Anton Petrunin}
\nofootnote{A.~Petrunin was partially supported by Simons Foundation grant \#584781.}

\newcommand{\Addresses}{{\bigskip\footnotesize
Anton Petrunin, \par\nopagebreak\textsc{Department of Mathematics, PSU, University Park, PA 16802, USA}
\par\nopagebreak
\textit{Email}: \texttt{petrunin@math.psu.edu}
}}

\date{}

\maketitle

Suppose $s\: X\to Y$ is a continuous map from a topological space $X$ to a metric space $Y$.
Recall that the pull-back metric $(x,x')\mapsto |xx'|_s$ is defined as the exact lower bound on lengths of $s\circ\alpha$ for all paths from $x$ to $x'$ in $X$.

In \cite{petrunin-metric-min} the metric minimizing map has to be defined as 
a continuous mapping $s\: D \to M$ such that (1) its pull-back metric $(x,x')\mapsto |xx'|_s$ is continuous and (2) there is no mapping $s'\: D \to M$ such that
$s'|_{\partial D} \equiv s|_{\partial D}$, $|xx'|_{s'} \le |xx' |_s$ for any two points $x, x' \in D$, and the inequality is strict for at least one pair $(x,x')$.

Originally, instead of continuity of $(x,x')\mapsto |xx'|_s$, I assumed only that the disc $D$ equipped with the pull-back metric is compact;
evidently, this is a weaker condition.

The sketch of proof of the main theorem \cite[2.2]{petrunin-metric-min} used the continuity implicitly.
An alternative proof of the case $k=0$ is given in \cite[9.2]{petrunin-stadler};
this proof can be modified in a straightforward way to prove \cite[2.2]{petrunin-metric-min}.

It remains open whether compactness alone is sufficient,
but it is sufficient for another natural definition of pull-back metric \cite[9.1]{petrunin-stadler}.

I would like to thank Stephan Stadler for pointing out this error.

\begin{thebibliography}{52}

\bibitem{petrunin-metric-min} Anton Petrunin,
\href{https://www.ams.org/journals/era/1999-05-07/S1079-6762-99-00059-1/}{\textit{Metric minimizing surfaces.}}
Electron. Res. Announc. Amer. Math. Soc. 5 (1999), 47--54.

\bibitem{petrunin-stadler} Anton Petrunin, Stephan Stadler
\textit{Metric minimizing surfaces revisited.} 
\texttt{arXiv:1707.09635 [math.DG]}.


\end{thebibliography}

\Addresses

\end{document}

??? check D --> \DD
